When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated description of SCA plot

All NASA-TLX subscale scores increased across $n$-back levels, so evidence was in favour of H1c.
The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.

@@

When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per $n$-back level.

@@

```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

>>>>

All NASA-TLX subscale scores increased across $n$-back levels, so evidence was in favour of H1c.
Ratings on the effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.

@@

When asking participants what motivated their decisions in the cognitive effort discounting paradigm, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per $n$-back level.

@@

```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a). The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect. The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
